---
title: "MAT381E-Homework 2"
author: "Mahmud Turab Karakaş"
date: "`r format(Sys.Date(), '%B %e, %Y')`"
output:
  html_document: default
  pdf_document: default
---


**Necessary** packages included in the project.  
```{r, warning=FALSE, message=FALSE}
library(rvest)
library(sf)
library(dplyr)
library(leaflet)
library(htmlwidgets)
```


Files with **.zip** extension are extracted into files.  
```{r, warning=FALSE, message=FALSE}
#unzip the contents in './data/turkey_administrativelevels0_1_2.zip' and save unzipped content in './data/turkey_administrativelevels0_1_2'
unzip(zipfile = "./data/zip/turkey_administrativelevels0_1_2.zip", exdir = "./data/turkey_administrativelevels0_1_2")

#unzip the contents in './data/turkey_centeralpoints_1_2.zip' and save unzipped content in './data/turkey_centralpoints_1_2'
unzip(zipfile = "./data/zip/turkey_centeralpoints_1_2.zip", exdir = "./data/turkey_centralpoints_1_2")
```

Data with **sf structure** was obtained with the **st_read** function.  
```{r, warning=FALSE, message=FALSE}
tur_polbnda_adm1_sf= st_read("data/turkey_administrativelevels0_1_2/tur_polbnda_adm1.shp")
tur_pntcntr_adm1_sf = st_read("data/turkey_centralpoints_1_2/tur_pntcntr_adm1.shp")
```

The web page with the specified url has been captured for **Web Scraping** process.  
```{r, warning=FALSE, message=FALSE}
url = "https://covid19.saglik.gov.tr/"

html = read_html(url)
```


Data were obtained from the table on the web page with the help of various functions.  
```{r, warning=FALSE, message=FALSE}
table_data = html %>% 
              html_elements("table") %>%
                .[[1]] %>%
                  html_table()
```


A conversion operation was performed for a variable in the data named **table_data**.  
```{r, warning=FALSE, message=FALSE}
#The variable named Sayı has been converted from character data type to numeric data type.
table_data$Sayı = as.numeric(gsub(",",".", table_data$Sayı))
```



A column named **Category** has been added to **table_data**.  
```{r, warning=FALSE, message=FALSE}
#The column named Category, which has an ordered factor structure,
# is filled with values corresponding to the specified conditions.
table_data = table_data %>%
                      mutate(Category = case_when(0<=Sayı & Sayı<=51 ~ "1",
                                                  51<Sayı & Sayı<=150 ~ "2",
                                                  150<Sayı & Sayı<=200 ~ "3",
                                                  200<Sayı & Sayı<=250 ~ "4",
                                                  250<Sayı ~ "5")) %>%
                        mutate(Category = factor(Category,
                                                 levels=c("1",
                                                          "2",
                                                          "3",
                                                          "4",
                                                          "5"),
                                                 ordered = TRUE))
```



A sub-data including the names of the provinces in Turkey and the geometry features of these provinces was created.  
```{r, warning=FALSE, message=FALSE}
#The variable containing the names of the provinces has been renamed to "İl Adı".
geometry_of_provinces = tur_polbnda_adm1_sf %>%
                          select(adm1_tr) %>%
                            rename("İl Adı" = "adm1_tr")
```


Necessary changes have been made so that the names of the provinces in the **table_data** and **geometry_of_provinces** are in the same order.  
```{r, warning=FALSE, message=FALSE}
table_data[c(48,49,50,51,68,69,70,71,72),] = table_data[c(51,48,49,50,71,68,69,72,70),]
```


The spelling of city names in **table_data** and **geometry_of_provinces** has been made the same.  
```{r, warning=FALSE, message=FALSE}
geometry_of_provinces[,"İl Adı"] = table_data[,"İl Adı"]
```


By merging the **table_data** and **geometry_of_provinces**, the data to be used in the **visualization** of the map is obtained.  
```{r, warning=FALSE, message=FALSE}
map_data = merge(geometry_of_provinces,table_data)
```


**Labels** that will appear when hovering over provinces on the map have been created.  
```{r, warning=FALSE, message=FALSE}
labels <-  sprintf("<strong>%s</strong><br/>
                    <strong> %s</strong>", map_data$"İl Adı", map_data$Sayı) %>%
                    lapply(htmltools::HTML)
```


A sequential color palette was created with colors corresponding to the specified levels.    
```{r, warning=FALSE, message=FALSE}
#Colors are taken from the map requested from us for each level specified with the help of the colorzilla plugin in Chrome.
pal_col = colorFactor(palette = c("#DAD9D7","#D1D0CE","#9C9C9C","#858585","#7A7878"), levels = c("1","2","3","4","5") ,ordered = TRUE)
```


A map was created using the data named **map_data**.  
```{r, warning=FALSE, message=FALSE}
map = map_data %>%
         leaflet() %>%
          addPolygons(color = "white",
                      weight = 1,
                      fillColor = ~pal_col(Category),
                      fillOpacity = 1,
                      smoothFactor = 1,
                      label = labels,
                      labelOptions = labelOptions(style = list("color" = "white", #for popup label
                                                               "background-color" = "#1B888C",
                                                               "border-color" = "#1B888C",
                                                               "padding" = "20px"),
                                                  textsize = "15px",
                                                  direction = "auto"),
                      highlight = highlightOptions(weight = 1,
                                                   fillColor = "#0E5C59",
                                                   bringToFront = TRUE)) %>% 
            addLabelOnlyMarkers(lng = tur_pntcntr_adm1_sf$longitude,
                                lat = tur_pntcntr_adm1_sf$latitude,
                                label = ~Sayı,
                                labelOptions = labelOptions(noHide = T, 
                                                            direction = "center",
                                                            textsize = "9px",
                                                            style = list("color" = "white",
                                                                         "background-color" = "#0E5C59",
                                                                         "border-color" = "#0E5C59",
                                                                         "border-radius" = "35%",
                                                                         "padding" = "0px"))) %>%
              addLegend(position = "bottomright",
                        pal = pal_col,  
                        values = ~ Category,  
                        title = 'İllere göre Haftalık Vaka Sayısı (100 binde)') 


map
```


```{r}
saveWidget(map, file="map.html")
```

